---
title: "DemandCurve"
author: "Teodora"
date: "2024-12-13"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1)Loading file 
-If you have an issue with loading the csv file after pasting the file location, it is because in the folder, the source is given with backslashes, but R does not read that. You should replace every backslash (\) with either a forward slash (/) or a double backslash (\\). 
```{r}
library(tidyverse)
in_cons_data<-read_csv("C:/Users/likis/OneDrive/Desktop/Microeconomics/PP440/Problem Set 1 - PP440 Data.csv")
```

2)Manipulating the data
-Right now, there is consumer data in 3 columns (indicating the willingness to purchase for each next increment, out of 3 increments). I will instead transform it to have all consumer demand data in one column. 
```{r}
library(dplyr) #loading so i can use pipes
cons_d<-in_cons_data %>%
  pivot_longer(
    cols = contains("SSBB"),  # Dynamically select columns containing "SSBB"
    names_to = "SSBB_Type",   # New column to store the column names (e.g., First_SSBB, etc.)
    values_to = "Value"       # New column to store the values from the selected columns
  )
cons_d
```

3)Value counts

```{r}
value_counts <- cons_d %>%
  arrange(desc(Value)) %>% #arranging in descending order of Price (descending order of "Value" column, so that the following operations work fine, also very important for the step graph)
  mutate(GreaterCount = sapply(Value, function(x) sum(Value > x)), #column of quantity demanded at a price greater than a given price (where price is in "Value") 
         GreaterOrEqualCount = sapply(Value, function(x) sum(Value >= x)), #column of quantity demanded at a price greater or equal to a given price (where price is in "Value") 
         LeadValue = lead(Value)) %>% #creating leads of quantity (needed for vertical segments of step plot)
  distinct(Value, GreaterOrEqualCount, GreaterCount, LeadValue)

value_counts
```

4)Creating plot
```{r}
library(ggplot2)

# Plot the step graph with customized line appearances
ggplot() +
  # Horizontal segments as dashed lines
  geom_segment(data = value_counts,
               aes(x = GreaterCount, xend = GreaterOrEqualCount, y = Value, yend = Value),
               linetype = "dashed", color = "black", size = 0.8) +
  # Vertical segments as solid lines
  geom_segment(data = value_counts,
               aes(x = GreaterOrEqualCount, xend = GreaterOrEqualCount, y = Value, yend = LeadValue), size = 1) +
  #Adding red dot indicating "when indifferent, buy"
  geom_point(data = value_counts, aes(x=GreaterOrEqualCount, y=Value), color = "red")+
  # Labels and theme
  labs(
    title = "Inverse Demand Curve",
    x = "Quantity of SSBBs",
    y = "Price of SSBBs"
  ) +
  theme_minimal()
```

