---
title: "terrorism_populism_ttm"
author: 'teodora-margaritova'
date: "2024-03-23"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
setwd("C:/Users/likis/OneDrive/Desktop/GV482/Summative")
library(haven)
popter<-read_dta("PopulismTerrorism.dta")
```

#MODIFICATIONS TO DATA SET

```{r}
popter <- popter[complete.cases(popter$populationY1), ]

#Creating a function to aggregate values of a given variable, for all 4 years leading up to the election.For example, Total4HomeIslClaim takes the sum of all claimed islamic terrorist attacks that happened in the 4 years leading to an election in a given country.
library(tidyverse)
createTotal4Variable <- function(prefix) {
  # Selecting columns starting with the specified prefix
  selected_columns <- select(popter, starts_with(prefix))
  # Converting selected columns to numeric, replacing NA values with 0
  selected_columns_numeric <- apply(selected_columns, 2, function(x) as.numeric(ifelse(is.na(x), 0, x)))
  # Summing across rows, handling NA values
  total_variable <- rowSums(selected_columns_numeric, na.rm = TRUE)
  # Assigning the total variable to a new column in the dataset
  popter[[paste0("Total4", prefix)]] <- total_variable
  return(popter)
}

variables <- c("HomeAttacks", "Homenkill", "Homenwound", "Homeleftproxy", "Homenkill_left", "Homenwound_left","Homerightproxy", "Homenkill_right", "Homenwound_right", "HomeIslClaim", "Homenkill_IslCl", "Homenwound_IslCl", "HomeIslPoss", "Homenkill_IslPoss", "Homenwound_IslPoss")

for (var in variables) {
  popter <- createTotal4Variable(var)
}

popter <- popter %>%
  mutate(
    PopulistRight = as.numeric(PopulistRight),
    PopulistLeft = as.numeric(PopulistLeft)
  ) %>%
  # Recalculate PopulistTot
  mutate(PopulistTot = rowSums(select(., PopulistRight, PopulistLeft), na.rm = TRUE))

#Creating lag variables for PopulistRight, PopulistLeft, PopulistTot
popter <- popter %>% 
  arrange(Country, Year) %>%
  group_by(Country) %>% 
  mutate(
    PopulistRight_Lag1 = lag(PopulistRight),
    PopulistLeft_Lag1 = lag(PopulistLeft),
    PopulistTot_Lag1 = lag(PopulistTot),
    PopulistRight_Lag2 = lag(PopulistRight, 2),
    PopulistLeft_Lag2 = lag(PopulistLeft, 2),
    PopulistTot_Lag2 = lag(PopulistTot, 2),
    PopulistRight_Lag3 = lag(PopulistRight, 3),
    PopulistLeft_Lag3 = lag(PopulistLeft, 3),
    PopulistTot_Lag3 = lag(PopulistTot, 3),
    PopulistRight_Lag4 = lag(PopulistRight, 4),
    PopulistLeft_Lag4 = lag(PopulistLeft, 4),
    PopulistTot_Lag4 = lag(PopulistTot, 4),
    PopulistRight_Lag5 = lag(PopulistRight, 5),
    PopulistLeft_Lag5 = lag(PopulistLeft, 5),
    PopulistTot_Lag5 = lag(PopulistTot, 5)
  )

# Creating a template data frame with all combinations of Country and Year
countries <- unique(popter$Country)
years <- 1977:2020
template_df <- expand.grid(Country = countries, Year = years)

# Merging the template data frame with the original data frame
merged_df <- left_join(template_df, popter, by = c("Country", "Year"))

# Sorting the data by Country and Year, and grouping by Country
gpopt <- merged_df %>% 
  arrange(Country, Year) %>%
  group_by(Country)

#Creating lead variables for HomeIslClaimY2, HomeIslClaimY3, and HomeIslClaimY4,and creating a merged variable combining them into one variable M_HomeIslClaim, which shows the number of attacks in a given year, in a given country
gpopt <- gpopt %>%
  mutate(
    Lead_HomeIslClaimY2 = lead(HomeIslClaimY2),
    Lead2_HomeIslClaimY3 = lead(HomeIslClaimY3, n = 2),
    Lead3_HomeIslClaimY4 = lead(HomeIslClaimY3, n = 3),
    M_HomeIslClaim = coalesce(HomeIslClaimY1, Lead_HomeIslClaimY2, Lead2_HomeIslClaimY3, Lead3_HomeIslClaimY4))

gpopt <- gpopt %>%
    mutate(
      Lead_Homenkill_IslClY2 = lead(Homenkill_IslClY2),
      Lead2_Homenkill_IslClY3 = lead(Homenkill_IslClY3, n = 2),
      Lead3_Homenkill_IslClY4 = lead(Homenkill_IslClY4, n = 3),
      M_HomeIslClaim_nkill = coalesce(Homenkill_IslClY1,Lead_Homenkill_IslClY2, Lead2_Homenkill_IslClY3, Lead3_Homenkill_IslClY4))
  
  gpopt <- gpopt %>%
    mutate(
      Lead_Homenwound_IslClY2 = lead(Homenwound_IslClY2),
      Lead2_Homenwound_IslClY3 = lead(Homenwound_IslClY3, n = 2),
      Lead3_Homenwound_IslClY4 = lead(Homenwound_IslClY4, n = 3),
      M_HomeIslClaim_nwound = coalesce(Homenwound_IslClY1,Lead_Homenwound_IslClY2, Lead2_Homenwound_IslClY3, Lead3_Homenwound_IslClY4)) 
  
  gpopt <- gpopt %>%
  mutate(
    Lead_HomeAttacksY2 = lead(HomeAttacksY2),
    Lead2_HomeAttacksY3 = lead(HomeAttacksY3, n = 2),
    Lead3_HomeAttacksY4 = lead(HomeAttacksY3, n = 3),
    M_HomeAttacks = coalesce(HomeAttacksY1, Lead_HomeAttacksY2, Lead2_HomeAttacksY3, Lead3_HomeAttacksY4))

gpopt <- gpopt %>%
    mutate(
      Lead_HomenkillY2 = lead(HomenkillY2),
      Lead2_HomenkillY3 = lead(HomenkillY3, n = 2),
      Lead3_HomenkillY4 = lead(HomenkillY4, n = 3),
      M_Homenkill = coalesce(HomenkillY1,Lead_HomenkillY2, Lead2_HomenkillY3, Lead3_HomenkillY4))
  
  gpopt <- gpopt %>%
    mutate(
      Lead_HomenwoundY2 = lead(HomenwoundY2),
      Lead2_HomenwoundY3 = lead(HomenwoundY3, n = 2),
      Lead3_HomenwoundY4 = lead(HomenwoundY4, n = 3),
      M_Homenwound = coalesce(HomenwoundY1,Lead_HomenwoundY2, Lead2_HomenwoundY3, Lead3_HomenwoundY4)) %>%ungroup()

#Removing objects i won't need
rm(merged_df, template_df)
```

#DESCRIPTIVE STATISTICS, PLOTS


```{r}
library(TAM)
library(modelsummary)
summary_statistics <- function(data, variables) {
  summary_list <- list()
  for (var in variables) {
    var_data <- na.omit(data[[var]])
    if (length(var_data) == 0) {
      cat("Variable", var, "contains only missing values.\n")
      next
    }
    n <- length(var_data)
    mean_uw <- mean(var_data)
    mean_w <- weighted.mean(var_data, w = popter$populationY1[!is.na(data[[var]])])
    sd_uw <- sd(var_data)
    sd_w <- TAM::weighted_sd(var_data, w = popter$populationY1[!is.na(data[[var]])])
    min_uw <- min(var_data)
    q1_uw <- quantile(var_data, 0.25)
    q1_w <- TAM::weighted_quantile(var_data, w = popter$populationY1[!is.na(data[[var]])], prob = 0.25)
    q3_uw <- quantile(var_data, 0.75)
    q3_w <- TAM::weighted_quantile(var_data, w = popter$populationY1[!is.na(data[[var]])], prob = 0.75)
    max_uw <- max(var_data)
    
    summary_list[[var]] <- data.frame(
      "Variable" = var,
      "Number of Observations" = n,
      "Mean" = mean_uw,
      "Weighted Mean" = mean_w,
      "Standard Deviation" = sd_uw,
      "Weighted Standard Deviation" = sd_w,
      "Minimum" = min_uw,
      "1st Quartile" = q1_uw,
      "Weighted 1st Quartile" = q1_w,
      "3rd Quartile" = q3_uw,
      "Weighted 3rd Quartile" = q3_w,
      "Maximum" = max_uw
    )
  }
  summary_df <- do.call(rbind, summary_list)
  return(summary_df)
}

# Example usage
sdf <- summary_statistics(popter, c("PopulistRight", "HomeIslClaimY1", "HomeIslClaimY2", "HomeIslClaimY3", "HomeIslClaimY4", "Homenkill_IslClY1", "Homenkill_IslClY2", "Homenkill_IslClY3", "Homenkill_IslClY4", "Homenwound_IslClY1", "Homenwound_IslClY2", "Homenwound_IslClY3", "Homenwound_IslClY4"))


descrs<-datasummary_df(sdf, output="latex")
descrs
```


```{r}
library(ggplot2)
subset_gpopt <- gpopt %>%
  filter(!is.na(M_HomeIslClaim_nwound) & 
         !is.na(M_HomeIslClaim_nkill) &
         !is.na(M_HomeIslClaim)) %>%
  select(Year, M_HomeIslClaim_nwound, M_HomeIslClaim_nkill, M_HomeIslClaim)

subset_gpopt_cumsum <- subset_gpopt %>%
  mutate(M_HomeIslClaim_nwound_cumsum = cumsum(M_HomeIslClaim_nwound),
         M_HomeIslClaim_nkill_cumsum = cumsum(M_HomeIslClaim_nkill),
         M_HomeIslClaim_cumsum = cumsum(M_HomeIslClaim))

subset_gpopt_sorted <- subset_gpopt %>%
  arrange(Year)

subset_gpopt_cumsum <- subset_gpopt_sorted %>%
  mutate(M_HomeIslClaim_nwound_cumsum = cumsum(M_HomeIslClaim_nwound),
         M_HomeIslClaim_nkill_cumsum = cumsum(M_HomeIslClaim_nkill),
         M_HomeIslClaim_cumsum = cumsum(M_HomeIslClaim))

# Create the plot for M_HomeIslClaim_cumsum
plot1<-ggplot(subset_gpopt_cumsum, aes(x = Year, y = M_HomeIslClaim_cumsum)) +
  geom_line(color = "darkgreen") +
  labs(
       x = "Year",
       y = "Number of Islamic Attacks") +
  theme_minimal()+
  theme(legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.3),
        axis.title.y = element_text(margin = margin(t = 0, r = 8, b = 0, l = 0)))
plot1

# Create the plot for M_HomeIslClaim_nkill_cumsum
plot2<-ggplot(subset_gpopt_cumsum, aes(x = Year, y = M_HomeIslClaim_nkill_cumsum)) +
  geom_line(color = "blue") +
  labs(       x = "Year",
       y = "Number of killings") +
  theme_minimal()+
  theme(legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.3),
        axis.title.y = element_text(margin = margin(t = 0, r = 8, b = 0, l = 0)))
plot2

# Create the plot for M_HomeIslWound_cumsum
plot3<-ggplot(subset_gpopt_cumsum, aes(x = Year, y = M_HomeIslClaim_nwound_cumsum)) +
  geom_line(color = "red") +
  labs(
       x = "Year",
       y = "Number of woundings") +
  theme_minimal()+
  theme(legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.3),
        axis.title.y = element_text(margin = margin(t = 0, r = 8, b = 0, l = 0)))
plot3

```

#PLOT OF AVERAGE POPULIST VOTE SHARE PER YEAR
```{r}
#Calculating average right and left wing populist vote share per year, for all units
library(dplyr)
av_popright <- aggregate(PopulistRight ~ Year, popter, FUN = function(x) round(mean(x), digits = 2))
av_popleft <- aggregate(PopulistLeft ~ Year, popter, FUN = function(x) round(mean(x), digits=2))
ds <- merge(av_popright, av_popleft, by = "Year", all = TRUE)
ds$PopulistTot <- rowSums(select(ds, PopulistRight,PopulistLeft))
rm(av_popright, av_popleft)

#Creating the plot for average vote share per year, with PopulistRight vote share, PopulistLeft vote share, and Total Populist Vote Share
library(ggplot2)
ggplot(ds, aes(x = Year)) +
  geom_area(aes(y = PopulistRight, fill = "Right-wing populism"), alpha = 1) +
  geom_area(aes(y = PopulistLeft, fill = "Left-wing populism"), alpha = 1) +
  geom_area(aes(y = PopulistTot, fill = "Total populism"), alpha = 0.5) +
  scale_fill_manual(values = c("Right-wing populism" = "aquamarine3", 
                                "Left-wing populism" = "coral2", 
                                "Total populism" = "burlywood"),
                    labels = c("Right-wing populism", "Left-wing populism", "Total populism")) +
  labs(x = "Year", y = "Average Populist Vote Share(%)",fill = NULL) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.background = element_rect(fill = "white"),
        plot.title = element_text(hjust = 0.5))
```

#Collapsing each of the different specifications for all 4 years (takes the sum of the variables 1,2,3,and 4 years before the election)
```{r}
country_c <- unique(popter$Country)
pref <- c("Attacks", "nkill", "nwound", "leftproxy", "nkill_left", "nwound_left","rightproxy", "nkill_right", "nwound_right", "IslClaim", "nkill_IslCl", "nwound_IslCl", "IslPoss", "nkill_IslPoss", "nwound_IslPoss")
```


#CREATING BORDER CONTROLS
```{r}
bordervar <- function(gpopt, country_c, pref, suffix) {
  # Loop over each prefix
  for (prefix in pref) {
    # Empty vector to store the results for the current prefix
    results <- numeric(nrow(gpopt))
    
    # Loop over each country code
    for (country_code in country_c) {
      # Getting Border variable
      border_var <- gpopt[[paste0("Border", country_code)]]
      # Getting terrorism variable with the specified year
      prefix_var <- gpopt[[paste0(prefix, country_code, suffix)]]
      # Product of Border and prefix variables
      results <- results + border_var * prefix_var
    }
    
    # Add the sum of results as a new variable in gpopt
    gpopt[[paste0("Border", suffix, prefix, "_sum")]] <- results
  }
  
  return(gpopt)
}

# Getting Border results for Y1
gpopt <- bordervar(gpopt, country_c, pref, "Y1")

# Getting Border results for Y2
gpopt <- bordervar(gpopt, country_c, pref, "Y2")

# Getting Border results for Y3
gpopt <- bordervar(gpopt, country_c, pref, "Y3")

# Getting Border results for Y4
gpopt <- bordervar(gpopt, country_c, pref, "Y4")

gpopt$BorderIslCl <- rowSums(gpopt[, paste0("BorderY", 1:4, "IslClaim_sum")])
gpopt$Bordernk_IslCl <- rowSums(gpopt[, paste0("BorderY", 1:4, "nkill_IslCl_sum")])
gpopt$Bordernw_IslCl <- rowSums(gpopt[, paste0("BorderY", 1:4, "nwound_IslCl_sum")])
```

#CREATING ECONOMIC AND DEMOGRAPHIC CONTROLS

```{r}
ecc<-"+UnemploymentY1+GrowthY1+Export_penetrationY1+Import_penetrationY1"
demc<-"+Immigration_percentY1+Emigration_percentY1"
```

#Weighted regressions with IslClaim collapsed over 4 years

```{r}
library(fixest)
t<- "| Country + Year"
lt <- "+ PopulistRight_Lag1|Country + Year"
lt2 <- "+ PopulistRight_Lag1+PopulistRight_Lag2|Country + Year"
lt3 <- "+ PopulistRight_Lag1+PopulistRight_Lag2+PopulistRight_Lag3|Country + Year"
  
#HOMEISLCLAIM weighted regressions

bc<-"PopulistRight ~ Total4HomeIslClaim"

#No controls
riscl1<-feols(as.formula(paste0(bc,t)), data=gpopt, weights=gpopt$populationY1)
summary(riscl1)

#Demographic and economic controls
riscl2<-feols(as.formula(paste0(bc,demc, ecc, t)), data=gpopt, weights=gpopt$populationY1)
summary(riscl2)

#Border, demographic and economic controls 
riscl3<-feols(as.formula(paste0(bc,demc, ecc,"+BorderIslCl", t)), data=gpopt, weights=gpopt$populationY1)
summary(riscl3)

#Border, demographic and economic controls, lag1
riscl4<-feols(as.formula(paste0(bc,demc, ecc,"+BorderIslCl", lt)), data=gpopt, weights=gpopt$populationY1)
summary(riscl4)

#Border, demographic and economic controls, lag2
riscl5<-feols(as.formula(paste0(bc,demc, ecc,"+BorderIslCl", lt2)), data=gpopt, weights=gpopt$populationY1)
summary(riscl5)

#Border, demographic and economic controls, lag3
riscl6<-feols(as.formula(paste0(bc,demc, ecc,"+BorderIslCl", lt3)), data=gpopt, weights=gpopt$populationY1)
summary(riscl6)

library(tibble)
library(modelsummary)

rows <- tribble(~term, ~estimate, ~control1, ~control4, ~control5, ~control6, ~control7,
                'Specifications', '', '','','','','',
                'Economic controls', 'No','Yes','Yes','Yes','Yes','Yes',
                'Demographic controls','No','Yes','Yes','Yes','Yes', 'Yes',
                'FE: Country','Yes','Yes','Yes','Yes','Yes','Yes',
                'FE: Year','Yes','Yes','Yes','Yes','Yes', 'Yes',
                'Weights', 'Yes', 'Yes', 'Yes', 'Yes', 'Yes', 'Yes',
                'Fit statistics', '', '','','','','')

attr(rows, 'position') <- c(11,12,13,14,15,16,17)

#Table
modelssc <- list(riscl1, riscl2, riscl3, riscl4, riscl5, riscl6)

# Generate the table
tabb1 <- modelsummary(
  modelssc, 
  coef_omit = c(2,3,4,5,6,7), 
  output = "html", 
  stars = T, 
  gof_omit = 'R2 Within|R2 Within Adj.|AIC|BIC|RMSE|FE: Country|FE: Year',
  add_rows = rows)
tabb1
```


#Weighted regressions with nkill_IslClaim collapsed over 4 years


```{r}
#HOMENKILL_ISLCL weighted regressions

bck<-"PopulistRight ~ Total4Homenkill_IslCl"

#No controls
risclk1<-feols(as.formula(paste0(bck,t)), data=gpopt, weights=gpopt$populationY1)
summary(risclk1)

#Demographic and economic controls
risclk2<-feols(as.formula(paste0(bck,demc, ecc, t)), data=gpopt, weights=gpopt$populationY1)
summary(risclk2)

#Border, demographic and economic controls 
risclk3<-feols(as.formula(paste0(bck,demc, ecc,"+Bordernk_IslCl", t)), data=gpopt, weights=gpopt$populationY1)
summary(risclk3)

#Border, demographic and economic controls, lag1
risclk4<-feols(as.formula(paste0(bck,demc, ecc,"+Bordernk_IslCl", lt)), data=gpopt, weights=gpopt$populationY1)
summary(risclk4)

#Border, demographic and economic controls, lag2
risclk5<-feols(as.formula(paste0(bck,demc, ecc,"+Bordernk_IslCl", lt2)), data=gpopt, weights=gpopt$populationY1)
summary(risclk5)

#Border, demographic and economic controls, lag3
risclk6<-feols(as.formula(paste0(bck,demc, ecc,"+Bordernk_IslCl", lt3)), data=gpopt, weights=gpopt$populationY1)
summary(risclk6)

#Table
modelssc2 <- list(risclk1, risclk2, risclk3, risclk4, risclk5, risclk6)

# Generate the table
tabb2 <- modelsummary(
  modelssc2, 
  coef_omit = c(2,3,4,5,6,7), 
  output = "latex", 
  stars = T, 
  gof_omit = 'R2 Within|R2 Within Adj.|AIC|BIC|RMSE|FE: Country|FE: Year',
  add_rows = rows)
tabb2
```
#Weighted regressions with nwound_IslClaim collapsed over 4 years

```{r}
#HOMEISLCLAIM_NWOUND weighted regressions

bcw<-"PopulistRight ~ Total4Homenwound_IslCl"

#No controls
risclw1<-feols(as.formula(paste0(bcw,t)), data=gpopt, weights=gpopt$populationY1)
summary(risclw1)

#Demographic and economic controls
risclw2<-feols(as.formula(paste0(bcw,demc, ecc, t)), data=gpopt, weights=gpopt$populationY1)
summary(risclw2)

#Border, demographic and economic controls 
risclw3<-feols(as.formula(paste0(bcw,demc, ecc,"+Bordernw_IslCl", t)), data=gpopt, weights=gpopt$populationY1)
summary(risclw3)

#Border, demographic and economic controls, lag1
risclw4<-feols(as.formula(paste0(bcw,demc, ecc,"+Bordernw_IslCl", lt)), data=gpopt, weights=gpopt$populationY1)
summary(risclw4)

#Border, demographic and economic controls, lag2
risclw5<-feols(as.formula(paste0(bcw,demc, ecc,"+Bordernw_IslCl", lt2)), data=gpopt, weights=gpopt$populationY1)
summary(risclw5)

#Border, demographic and economic controls, lag3
risclw6<-feols(as.formula(paste0(bcw,demc, ecc,"+Bordernw_IslCl", lt3)), data=gpopt, weights=gpopt$populationY1)
summary(risclw6)

#Table
modelssc3 <- list(risclw1, risclw2, risclw3, risclw4, risclw5, risclw6)

# Generate the table
tabb3 <- modelsummary(
  modelssc3, 
  coef_omit = c(2,3,4,5,6,7), 
  output = "latex", 
  stars = T, 
  gof_omit = 'R2 Within|R2 Within Adj.|AIC|BIC|RMSE|FE: Country|FE: Year',
  add_rows = rows)
tabb3
```

```{r}


gpopt$Lead_MHomeIslClaim <- lead(gpopt$M_HomeIslClaim)
gpopt$Lead2_MHomeIslClaim<-lead(gpopt$M_HomeIslClaim, n=2)
gpopt$Lead3_MHomeIslClaim<-lead(gpopt$M_HomeIslClaim, n=3)

tt<-"PopulistRight~Lead_MHomeIslClaim"
tt2<-"PopulistRight~Lead_MHomeIslClaim+Lead2_MHomeIslClaim"
tt3<-"PopulistRight~Lead_MHomeIslClaim+Lead2_MHomeIslClaim+Lead3_MHomeIslClaim"

leadr<-feols(as.formula(paste0(tt,demc,ecc,"+Bordernw_IslCl", t)), data=gpopt, weights=gpopt$populationY1)
summary(leadr)
leadr2<-feols(as.formula(paste0(tt2,demc,ecc,"+Bordernw_IslCl", t)), data=gpopt, weights=gpopt$populationY1)
summary(leadr2)
leadr3<-feols(as.formula(paste0(tt3,demc,ecc,"+Bordernw_IslCl", t)), data=gpopt, weights=gpopt$populationY1)
summary(leadr3)

leadmod<-list(leadr, leadr2, leadr3)

rowssl <- tribble(
  ~term, ~estimate, ~control1, ~control4,
  'Specifications', '', '', '',
  'Economic controls', 'Yes', 'Yes', 'Yes',
  'Demographic controls', 'Yes', 'Yes', 'Yes',
  'FE: Country', 'Yes', 'Yes', 'Yes',
  'FE: Year', 'Yes', 'Yes', 'Yes',
  'Weights', 'Yes', 'Yes', 'Yes',
  'Fit statistics', '', '', ''
)

attr(rowssl, 'position') <- c(23, 24,25,26, 27, 28,29)

modelsummary(leadmod, coef_omit = c(2,3,4,5,6,7), 
  output = "html", 
  stars = T, 
  gof_omit = 'R2 Within|R2 Within Adj.|AIC|BIC|RMSE|FE: Country|FE: Year',
  add_rows = rowssl)



```





